Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-05 WSSSPE1_report/WSSSPE1_summary_report.tex
listing software projects
adding to software usecase list
Section 3 Keynote: turn presentations and URLs into references

\section{Keynotes} \label{sec:keynotes}

\note{lead: Sou-Cheng (Terrya) Choi}

@@

The first
keynote\footnote{\url{http://wssspe.researchcomputing.org.uk/keynotes/\#bourne}}
was delivered by Philip E. Bourne of UCSD. The slides are available
online.\footnote{\url{www.slideshare.net/pebourne/a-recipe-for-sustainable-software}}
Philip is a basic biomedical scientist but has formed four software
companies. He also helped found PLOS and
PDB\footnote{\url{http://www.rcsb.org/pdb/home/home.do}}.  He is
working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and would serve as a key function of software in biomedical sciences.

Philip emphasized that Sustainability for software ``does not just
mean more money from Government.''  He noted that in places,
development in science has improved thanks to open source and Github,
but for the most part remains arcane. He argued that there is much we
can learn from the app-store model. He mentioned
BioJava\footnote{\url{http://biojava.org/wiki/Main_Page}} and
OpenScienceDataCloud\footnote{\url{https://www.opensciencedatacloud.org/}}
as distribution channels.  On a related note, Philip observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.

Philip shared with the audience a few real challenges he
encountered. First, he has looked into reproducibility in
computational biology, and has concluded that ``I have proved I cannot
reproduce research from my own lab''~\cite{Veretnik}.

@@

The second keynote\footnote{\url{http://is.gd/wssspe}} was by
 Arfon Smith\footnote{\url{http://arfon.org/}} of Github.

@@

Perhaps discuss sustained software use-cases and issues surrounding
them. Some examples could be mvapich, Galaxy, Swift, Cactus, etc.

>>>>

\section{Keynotes\note{lead: Sou-Cheng (Terrya) Choi}} \label{sec:keynotes}

@@

The first
keynote~\cite{WSSSPE1-keynote1}
was delivered by Philip E. Bourne of University of California, San Diego.  Bourne is a basic biomedical scientist but has formed four software
companies. He also helped found PLOS and
PDB\footnote{\url{http://www.rcsb.org/pdb/home/home.do}}.  He is
working on automating three-dimensional visualizations of cell
contents and molecular structures, a problem that has not been solved
and would serve as a key function of software in biomedical sciences.

Bourne's keynote presentation is entiled ``A Recipe for Sustainable Software''.
He emphasized that sustainability for software ``does not just
mean more money from Government.''  He noted that in places,
development in science has improved thanks to open source and Github,
but for the most part remains arcane. He argued that there is much we
can learn from the App Store model. He mentioned
BioJava\footnote{\url{http://biojava.org/wiki/Main_Page}} and
OpenScienceDataCloud\footnote{\url{https://www.opensciencedatacloud.org/}}
as distribution channels.  On a related note, Bourne observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.

Bourne shared with the audience a few real challenges he
encountered. First, he has looked into reproducibility in
computational biology, and has concluded that ``I have proved I cannot
reproduce research from my own lab''~\cite{Veretnik}.

@@

The second keynote~\cite{WSSSPE1-keynote2}\footnote{\url{}} was by
 Arfon Smith\footnote{\url{http://arfon.org/}} of Github.

@@

Perhaps discuss sustained software use-cases and issues surrounding
them. Following is a list of software projects discussed throughout the workshop:

\begin{itemize}
    \item github
    \item mvapich
    \item Cactus
    \item visTrails
    \item MINRES/QLP
    \item SimGrid
    \item Swift
    \item Galaxy
    \item FastMath and package managers
    \item R/qtl
    \item OWL/RDF
    \item AMR/multiphysics
    \item DUNE
    \item PAAS
    \item Gateways
    \item Globus-Genomics
\end{itemize}
